Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Devil-may-care censors.

% Censors that know no bounds: China on Google, Egypt, Pakistan with YouTube.

>>>>

Domain fronting derives part of its unblockability from the
high collateral damage of blocking the domain fronted through.
Fronting through \urll{www.google.com} to App Engine, for example,
is betting that censor will lack the temerity to block Google.
The Great Firewall of China called our bluff in June of 2014,
when it blocked access to all Google services~\cite{cn-google-block}.
In 2012, the government of Pakisten blocked to all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly ``turned off the net'' completely.
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
To block Google is an extreme measure,
probably out of reach of most censors.
Blocking all of the fronting-capable services listed in
Section~\ref{sec:survey} would be even harder.
